### 2020-05-26 README.Rmd
updated license info on readme

This library is provided for use under the Creative Commons by Attribution license ([CC BY 3.0](https://creativecommons.org/licenses/by/3.0/au/legalcode)) by the AIMS Datacentre for the [Australian Institute of Marine Science](https://www.aims.gov.au)

>>>>

`dataaimsr` is provided by the [Australian Institute of Marine Science](https://www.aims.gov.au) under the MIT License ([MIT](http://opensource.org/licenses/MIT)).
